### 2019-08-12 thesis.tex
*** empty log message ***

%\listoffigures{\thispagestyle{empty}}

@@

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface zone
where the outgoing pressure of the solar plasma balances the incoming pressure
from the interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017},
has an inner boundary, the \emph{termination shock}, which delimits the sphere
of absolute influence of the solar plasma. Beyond the termination shock, at
roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
heliosheath. In this region, the solar wind particles start being subjected to
increasing external pressure, transitioning to a subsonic, turbulent flow that
blends and interacts directly with the matter in the local interstellar medium
\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
boundaries described above, and the current location of both Voyager missions,
that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

The extension of the influence that the plasma ejected from the Sun has, puts
in perspective the fundamental role played by plasma physics in the solar and
space physics research. %% talk about some key processes

>>>>

\listoffigures{\thispagestyle{empty}}

@@

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface zone
where the outgoing pressure of the solar plasma balances the incoming pressure
from the interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017},
has an inner boundary, the \emph{termination shock}, which delimits the sphere
of absolute influence of the solar plasma. Beyond the termination shock, at
roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
\emph{heliosheath}. In this region, the solar wind particles start being subjected
to increasing external pressure, transitioning to a subsonic, turbulent flow that
blends and interacts directly with the matter in the local interstellar medium
\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
boundaries described above, and the current location of both Voyager missions,
that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

The fundamental questions of heliophysics start right in the Sun and the
magnetic dynamo processes involved in the generation and variability of
magnetic fields in the Sun, and how it determines the dynamics of the
11-year solar cycle of sunspots. The appearance of sunspots is a sign of
solar activity, characterized by solar flares and coronal mass ejections.

This enhanced flux of energetic particles and radiation have direct impact
in the \emph{space weather} around Earth, triggering geomagnetic storms
that
